### 2016-06-22 paper/numerical_experiments.tex
camera angle for paraview processing of domain breakdown, script to convert error breakdown into exo for paraview processing as well

The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively. We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
%
\begin{subequations}
\label{eq:cdvcdrHF3D}
\begin{align}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_rnu^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
u = 5 \quad &\text{on } \partial \Omega_{west}, \\
\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
\end{align} 
\end{subequations}
%
where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field. The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day. Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}. We have porosity $n=0.1$. The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions. Although the reaction term $k_rnu^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.

@@

We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, for a range of error tolerances. At each iteration, we choose the basis functions with the largest $10\%$ of the error for model refinement. All simulations are run on a single processor. Table~\ref{tab:ref3D} shows ...
%
\begin{tabular}{c|c|c|c|c|c}
Case & $\%HF$ & QoI & Relative Error (Estimated) & Relative Error (Actual) & Time (s) \\
LF & 0 & 1068856 &  &  &  \\
MF01 & 16.7 &  &  &  &  \\
MF02 & 29.0 &  &  &  &  \\
MF03 & 42.3 &  &  &  &  \\
HF & 100 & 547420 &  &  &  \\
\caption{...}
\end{tabular}

%previous 2D examples were toy problems were good illustrate something (error breakdown patterns), but too simple to really see any computational cost differences
%bigger steps in 3D problem because qoi region bigger?

>>>>

The two models share a box domain $\Omega(x_1,x_2,x_3)$ which is $2300$m, $1650$m, and $100$m long in the $x_1$, $x_2$, and $x_3$ directions, respectively. We will refer to the positive and negative directions in $x_1$ as ``east" and ``west", respectively. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by
%
\begin{subequations}
\label{eq:cdvcdrHF3D}
\begin{align}
\nabla\cdot(n\vec{V}u - nD\nabla u) + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:HFeq3D}\\
u = 5 \quad &\text{on } \partial \Omega_{west}, \\
\frac{\partial u}{\partial n} = 0 \quad &\text{on }\partial\Omega_{east}, \\
\hat{n}\cdot(n\vec{V}u - nD\nabla u) = 0 \quad &\text{on }\partial\Omega\backslash(\partial\Omega_{east}\cup\partial\Omega_{west}),
\end{align} 
\end{subequations}
%
where the state $u$ is the mass-fraction (in parts-per-billion) of some contaminant species and $f(q)$ is a source/sink field. The velocity field is a constant $\vec{V}=(2.1,0,0)$ m/day. Given this velocity field and letting the molecular diffusion be negligble, we follow \cite{Vestedetal93} to express the (diagonal) dispersion tensor $D$ as $D_{11}=\alpha_{LH}V_1$, $D_{22}=\alpha_{TH}V_1$, and $D_{33}=\alpha_{TV}V_1$, where $\alpha_{LH}=100$m, $\alpha_{TH}=40$m, and $\alpha_{TV}=4$m are the longitudinal horizontal, transverse horizontal, and transverse vertical dispersivities, respectively; the dispersivity values were drawn from within the range of observed values in various porous media \cite{Davis86}. We have porosity $n=0.1$. The reaction coefficient is $k_r=4.2\cdot10^{-4}$ 1/day, chosen from within the wide range of reaction-rate coefficients for second-order reactions. Although the reaction term $k_rnu^2$ does not correspond to any particular reaction of any particular species, we note that, in addition to second-order elementary reactions, a quadratic reaction term can appear in models of dissolution/precipitation processes in porous media \cite{Aha97} and biochemical degredation of petroleum hydrocarbons in soils \cite{Jack94}.

@@

We now present the results of solving the inference problem using Algorithm~\ref{alg:refSeries}, for a range of error tolerances. At each iteration, we choose the basis functions with the largest $10\%$ of the error for model refinement. All simulations are run on a single processor. Table~\ref{tab:ref3D} shows ...
%
\begin{table}[h]
\centering
\begin{tabular}{c|c|c|c|c|c}
\multirow{2}{*}{Case} & \multirow{2}{*}{$\%HF$} & \multirow{2}{*}{QoI} & Relative Error & Relative Error & \multirow{2}{*}{Time (s)} \\ 
& & & (Estimated) & (Actual) & \\ \hline
LF & 0 & 1068856 &  &  &  \\
MF01 & 16.7 &  &  &  &  \\
MF02 & 29.0 &  &  &  &  \\
MF03 & 42.3 &  &  &  &  \\
HF & 100 & 547420 &  &  &  \\
\end{tabular}
\caption{table of things}
\end{table}
